CudeleFS: Programmable Consistency and Durability\\in a Global Namespace

### 2017-03-31 paper/sections/1_introduction.tex
paper: noah section 2 comments
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[tb]
\centering
\includegraphics[width=0.5\textwidth]{figures/subtree-policies.png}
\caption{Administrators can assign consistency and durability policies to
subtrees to get the benefits of some of the state-of-the-art HPC architectures.
}\label{fig:subtree-policies}
\end{figure}

>>>>

\begin{figure}[tb]
\centering
\includegraphics[width=0.5\textwidth]{figures/subtree-policies.png}
\caption{Administrators can assign weaker consistency and durability policies
to subtrees to get the same performance benefits of state-of-the-art HPC
architectures. Applications that need stronger guarantees can still reside in
the same namespace.
}\label{fig:subtree-policies}
\end{figure}

### 2017-03-31 paper/sections/3_posix_overheads.tex
paper: noah section 2 comments
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[tb]
\centering
\includegraphics[width=1\linewidth]{./graphs/overhead-creates.png}
\caption{Create-heavy workloads (untar) incurr the highest disk, network, and
CPU utilization because of the consistency and durability demands of CephFS
.}\label{fig:overhead-creates}
\end{figure}

@@

To show how the file system behaves under high metadata load we use a
create-heavy workload. Create-heavy workloads are studied the most in HPC
research because of the checkpoint/restart use case but they also happen to
stress the underyling storage system the most.
Figure~\ref{fig:overhead-creates} shows the resource utilization of compiling
the Linux kernel.  The untar phase, which is characterized by many creates, has
the highest resource usage which suggests that it is stressing the consistency
and journalling subsystems of the metadata server the most. Traditional file
system techniques for improving performance, such as caching inodes, do not
help for create-heavy workloads.

In this section, we quantify the costs of strong consistency and global
durability in CephFS.  We use the kernel client so that we can find the true
create speed of the server; our experiments show a low CPU utilziation for the
clients which indicates that we are stressing the servers more.

@@

% what is durability
While durability is not specified by POSIX, users expect that their metadata is
safe. We define three types of durability: global, local, and none.  Global
durability means that the client or server can fail at any time and metadata
will not be lost. Local durability means that metadata can be lost if the
client or server fails and stays failed. None means that metadata is volatile
and that the system provides no guarantees when clients or servers fail.\\

% - sequential IO, trim redundant operations
\noindent\textbf{CephFS Design}: a journal of metadata updates that streams into
the resilient object store. Similar to LFS~\cite{rosenblum:acm1992-LFS} and
WAFL~\cite{hitz:wtec1994-WAFL} the metadata journal can grow to large sizes
ensuring (1) sequential writes into RADOS and (2) the ability for daemons to
trim redundant or irrelevent journal entries.  The journal is striped over
objects where multiple journal updates can reside on the same object. There are
two tunables for controlling the journal: the segment size and the number of
parallel segments that can be written in parallel. The former is memory bound
as larger segments take up more memory but can reduce the time spent journaling
and the latter is CPU bound.

@@

\noindent\textbf{Comparison to decoupled namespaces}: In BatchFS and DeltaFS,
as far as we can tell, when a client or server fails there is no recovery
scheme. For BatchFS, if a client fails when it is writing to the local
log-structured merged tree (implemented as an SSTable) then those batched
metadata operations are lost. For DeltaFS, if the client fails then on restart
the computation does the work again -- since the snapshots of the namespace are
never globally consistent and there is no ground truth.  On the server side,
BatchFS and DeltaFS use IndexFS. Again, IndexFS writes metadata to SSTables but
it is not clear whether they ever vacate memory, get written to disk, or are
flushed to the object store.

@@

Access to metadata in a POSIX-compliant file system is strongly consistent, so
reads and writes are globally ordered.  The synchronization and serialization
machinery needed to ensure that all clients see the same state has high
overhead.\\

@@

% benefits PROBLEM -- IS THIS THE METADATA PROTOCOL OR JUST THE OVERLOADEDNESS?
The benefits of caching the directory inode when creating files is shown in
Figure~\ref{fig:interfere-a}.  If only one client is creating files in a
directory (``isolated" curve on \(y1\) axis) then that client can lookup the
existence of new files locally before issuing a create request to the metadata
server. If another client starts creating files in the same directory
(``interfere" curve on \(y1\) axis) then the directory inode transitions out of
read caching and the first client must send \texttt{lookup()}s to the metadata
server (``interfere" curve on \(y2\) axis). These extra requests increase the
throughput of the ``interfere" curve because the metadata server can handle the
extra load but the overall performance decreases.  This degradation is shown in
Figure~\ref{fig:interfere-b}, where we scale the number of clients and show
increased runtime and variability. The performance is compared to a single
isolated client and he error bar is the standard deviation of the runtime of
all clients.  For the ``interfere" bars, each client creates files in private
directories and at 30 seconds we launch another process that creates files in
those directories.  For less than 7 clients, the runtime and deviation is worse
when clients interfere. At 7 clients, the metadata server is overloaded so the
directory caching in the ``isolated" bars has no benefit. Zooming in on runs
with 7 clients in Figure~\ref{fig:interfere-c} we see how different
interferring operations affect performance, again when compared to the
performance of a single isolate client.  ``create" has little effect but
``stat" and ``create many" cause noticeable slowdowns because of the extra work
they impose on the metadata server.\\

>>>>

\begin{figure}[tb]
\centering
\includegraphics[width=1\linewidth]{./graphs/overhead-creates.png}
\caption{Create-heavy workloads (untar) incurr the highest disk, network, and
CPU utilization because of the consistency and durability demands of
CephFS.}\label{fig:overhead-creates}
\end{figure}

@@

To show how the file system behaves under high metadata load we use a
create-heavy workload. Create-heavy workloads are studied the most in HPC
research because of the checkpoint/restart use case but they also happen to
stress the underyling storage system the most.
Figure~\ref{fig:overhead-creates} shows the resource utilization of compiling
the Linux kernel.  The untar phase, which is characterized by many creates, has
the highest resource usage which suggests that it is stressing the consistency
and journaling subsystems of the metadata server the most. Traditional file
system techniques for improving performance, such as caching inodes, do not
help for create-heavy workloads.

In this section, we quantify the costs of strong consistency and global
durability in CephFS. At the end of each subsection we compare the approach to
``decoupled namespaces", the technique in related work that detaches subtrees
from the global namespace to relax consistency/durability guarantees.  We use
the kernel client so that we can find the true create speed of the server; our
experiments show a low CPU utilziation for the clients which indicates that we
are stressing the servers more.

@@

% what is durability
While durability is not specified by POSIX, users expect that files they create
or modify survive failures.  We define three types of durability: global,
local, and none.  Global
durability means that the client or server can fail at any time and metadata
will not be lost. Local durability means that metadata can be lost if the
client or server stays down after a failure. None means that metadata is volatile
and that the system provides no guarantees when clients or servers fail. 
None is different than local durability because regardless of the type failure,
metadata will be lost when components die in a None configuration.\\

% - sequential IO, trim redundant operations
\noindent\textbf{CephFS Design}: a journal of metadata updates that streams into
the resilient object store. Similar to LFS~\cite{rosenblum:acm1992-LFS} and
WAFL~\cite{hitz:wtec1994-WAFL} the metadata journal is designed to grow to large which
ensures (1) sequential writes into the object store and (2) the ability for daemons to
trim redundant or irrelevent journal entries.  The journal is striped over
objects where multiple journal updates can reside on the same object. There are
two tunables for controlling the journal: the segment size and the number of
parallel segments that can be written in parallel. Unless the journal saturates 
memory or CPU resources, larger values for these tunables results in better
performance.

@@

\noindent\textbf{Comparison to decoupled namespaces}: In BatchFS and DeltaFS,
as far as we can tell, when a client or server fails there is no recovery
scheme. For BatchFS, if a client fails when it is writing to the local
log-structured merged tree (implemented as an SSTable) then those batched
metadata operations are lost. For DeltaFS, if the client fails then on restart
the computation does the work again -- since the snapshots of the namespace are
never globally consistent and there is no ground truth.  On the server side,
BatchFS and DeltaFS use IndexFS. IndexFS writes metadata to SSTables, which
initially reside in memory but are later to flushed to the underlying
distributed file system.

@@

Access to metadata in a POSIX-compliant file system is strongly consistent, so
reads and writes to the same inode or directory are globally ordered.  The
synchronization and serialization machinery needed to ensure that all clients
see the same state has high overhead.\\

@@

% benefits PROBLEM -- IS THIS THE METADATA PROTOCOL OR JUST THE OVERLOADEDNESS?
The benefits of caching the directory inode when creating files is shown in
Figure~\ref{fig:interfere-a}.  If only one client is creating files in a
directory (``isolated" curve on \(y1\) axis) then that client can lookup the
existence of new files locally before issuing a create request to the metadata
server. If another client starts creating files in the same directory
(``interfere" curve on \(y1\) axis) then the directory inode transitions out of
read caching and the first client must send \texttt{lookup()}s to the metadata
server (``interfere" curve on \(y2\) axis). These extra requests increase the
throughput of the ``interfere" curve because the metadata server can handle the
extra load but the overall performance decreases.  This degradation is shown in
Figure~\ref{fig:interfere-b}, where we scale the number of clients and show
increased runtime and variability. The performance is compared to a single
isolated client and the error bar is the standard deviation of the runtime of
all clients.  For the ``interfere" bars, each client creates files in private
directories and at 30 seconds we launch another process that creates files in
those directories.  For less than 7 clients, the runtime and deviation is worse
when clients interfere. At 7 clients, the metadata server is overloaded so the
directory caching in the ``isolated" bars has no benefit. Zooming in on runs
with 7 clients in Figure~\ref{fig:interfere-c} we see how different
interferring operations affect performance, again when compared to the
performance of a single isolate client.  ``create" has little effect but
``stat" and ``create many" cause noticeable slowdowns because of the extra work
they impose on the metadata server.\\
